---
title: "Homework 2"
author: "Ishrat Chowdhury"
date: "September 22, 2019"
output: html_document
---

Prompt:
 
Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

First lets find out a little bit more about Poisson Distribution:

```{r}
?ppois # pulls up manual 
```

Now that we know more about Poisson Distribution let's answer some questions!

  What is the probability that she will hear more than 8 calls during any given session?

```{r}
ppois(7, lambda=15, lower.tail = FALSE) 
  # We want to know probability so use ppois.
  # The lambda (mean) is 15 calls.
  # We want to know the probability of hearing more than 8 calls, the probability of hearing 7 or less calls is the lower tail, if lower tail is false we get the upper tail, which is the probability of 8 or more calls
```

  What is the probability that she will hear no calls in a session?

```{r}
ppois(0, lambda = 15)
  # Similar as before except now we do not need upper or lower tails since we are just looking for 0 calls; there is not lower tail to this and the upper tail to this is asking if she would hear more than 1 call.
```

  What is the probability that she will hear exactly 3 calls in a session?
  
```{r}
dpois(x=3, lambda = 15)
  #Now we use qpois because we want to know the probability of an exact number rather than a range
  #We want to know the probability of exactly 3 calls, while the lambda is still 15 calls
```

Plot the relevant Poisson mass function over the values in range 0 ??? x ??? 30.

First lets load some packages that will help us plot this
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(ggplot2)
library(dplyr)
```
 
```{r}
?barplot #barplot manual
x<-dpois(x=0:30, lambda = 15) #define dataset
barplot(x, xlab = "number of calls", ylab = "probability of calls", main = "Poisson mass function") #plot using defined dataset

  #use he barplot function here, when using historgram, probablites get plotted giving it a left skewed apperance. histogram also uses only vectors of numbers.
```

Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
w<-rpois(104, 15) 
  # 104 results is the n
  # lambda is still 15
w
```

Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
?hist
hist(w, xlim = c(0, 30), xlab = "number of calls", main = "Simulated Results mass function") #plot the results putting a limit from 0 to 30 on x
#this histogram is more left skewed than the previous one, this makes sense because it is representing actual random data rather than just the ideal situation
```
